### 2025-02-10 images/ansatz/quantikz/Full-CRX.tex
Mon 10 Feb 2025 17:00:20 EST poster/manuscript figures

%Full-CRX
\resizebox{\textwidth}{!}{
\begin{quantikz}
	\lstick{$q_0$}& \gate{RX} & \gate{RZ} &\ctrl{1}& \ctrl{2}&\ctrl{3}&\ctrl{4}&\gate{RX} &&&&\gate{RX}&&&&\gate{RX}& &&&\gate{RX}&&&&\\
	\lstick{$q_1$}& \gate{RX} & \gate{RZ} & \gate{RX} &&&& \ctrl{-1} & \ctrl{1} & \ctrl{2} &  \ctrl{3}&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&&&\\
	\lstick{$q_2$}& \gate{RX} & \gate{RZ} && \gate{RX}&&&&\gate{RX}&&& \ctrl{-2}&\ctrl{-1}&\ctrl{1}&\ctrl{2}&&&\gate{RX}&&&&\gate{RX}&&\\
	\lstick{$q_3$}& \gate{RX} & \gate{RZ} &&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}& \ctrl{1}&&&&\gate{RX}&\\
	\lstick{$q_4$}& \gate{RX} & \gate{RZ} &&&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&\ctrl{-4}&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}&\\
\end{quantikz}
}

>>>>

%Full-CRX(	\theta)
\resizebox{\textwidth}{!}{
\begin{quantikz}
	\lstick{$q_0$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &\ctrl{1}& \ctrl{2}&\ctrl{3}&\ctrl{4}&\gate{RX(	\theta)} &&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}& &&&\gate{RX(	\theta)}&&&&\\
	\lstick{$q_1$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} & \gate{RX(	\theta)} &&&& \ctrl{-1} & \ctrl{1} & \ctrl{2} &  \ctrl{3}&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&&\\
	\lstick{$q_2$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} && \gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&& \ctrl{-2}&\ctrl{-1}&\ctrl{1}&\ctrl{2}&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&\\
	\lstick{$q_3$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}& \ctrl{1}&&&&\gate{RX(	\theta)}&\\
	\lstick{$q_4$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&\ctrl{-4}&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}&\\
\end{quantikz}
}

### 2025-02-10 images/ansatz/quantikz/Full-CRZ.tex
Mon 10 Feb 2025 17:00:20 EST poster/manuscript figures

\begin{document}
%Full-CRZ
\resizebox{\textwidth}{!}{
	\begin{quantikz}
		\lstick{$q_0$}& \gate{RX} & \gate{RZ} &\ctrl{1}& \ctrl{2}&\ctrl{3}&\ctrl{4}&\gate{RZ} &&&&\gate{RZ}&&&&\gate{RZ}& &&&\gate{RZ}&&&&\\
		\lstick{$q_1$}& \gate{RX} & \gate{RZ} & \gate{RZ} &&&& \ctrl{-1} & \ctrl{1} & \ctrl{2} &  \ctrl{3}&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RZ}&&&\\
		\lstick{$q_2$}& \gate{RX} & \gate{RZ} && \gate{RZ}&&&&\gate{RZ}&&& \ctrl{-2}&\ctrl{-1}&\ctrl{1}&\ctrl{2}&&&\gate{RZ}&&&&\gate{RZ}&&\\
		\lstick{$q_3$}& \gate{RX} & \gate{RZ} &&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RZ}&&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}& \ctrl{1}&&&&\gate{RZ}&\\
		\lstick{$q_4$}& \gate{RX} & \gate{RZ} &&&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RX}&\ctrl{-4}&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}&\\
	\end{quantikz}
}

>>>>

\begin{document}
%Full-CRZ(	\theta)
\resizebox{\textwidth}{!}{
	\begin{quantikz}
		\lstick{$q_0$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &\ctrl{1}& \ctrl{2}&\ctrl{3}&\ctrl{4}&\gate{RZ(	\theta)} &&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}& &&&\gate{RZ(	\theta)}&&&&\\
		\lstick{$q_1$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} & \gate{RZ(	\theta)} &&&& \ctrl{-1} & \ctrl{1} & \ctrl{2} &  \ctrl{3}&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&&\\
		\lstick{$q_2$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} && \gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&& \ctrl{-2}&\ctrl{-1}&\ctrl{1}&\ctrl{2}&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&\\
		\lstick{$q_3$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}& \ctrl{1}&&&&\gate{RZ(	\theta)}&\\
		\lstick{$q_4$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&&&\gate{RX(	\theta)}&\ctrl{-4}&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}&\\
	\end{quantikz}
}

### 2025-02-10 images/encoders/quantikz/IQP.tex
Mon 10 Feb 2025 17:00:20 EST poster/manuscript figures

\documentclass[preview, border=1mm]{standalone}
\usepackage{tikz} %Format quantum circuits
\usetikzlibrary{quantikz2}%Format quantum circuits
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools,physics}
\def\myvdots{\ \vdots\ }

\begin{document}
\begin{quantikz} 
\lstick{$q_0$} & \gate{H} & \gate{R_{Z} (x_{0})} & \gate[2,disable auto height]{ZZ(x_{0},x_{1})} &  & \gate[3,disable auto height]{ZZ(x_{0},x_{2})} & \gate[5,disable auto height]{ZZ(x_{0},x_{n})}   & & &  \\ 
\lstick{$q_1$} & \gate{H} & \gate{R_{Z} (x_{1})} & & \gate[2,disable auto height]{ZZ(x_{1},x_{2})}  & & &  \gate[4,disable auto height]{ZZ(x_{1},x_{n})}  &  &\\ 
\lstick{$q_2$} & \gate{H} & \gate{R_{Z} (x_{2})} & & & & & & \gate[3,disable auto height]{ZZ(x_{2},x_{n})}  & \\ 
\setwiretype{n} \lstick{}  & \myvdots & \myvdots & \myvdots  & \myvdots & \myvdots & \\
\lstick{$q_n$}& \gate{H}  & \gate{R_{Z} (x_{n})} & & & & & & &\\
\end{quantikz}
\end{document}

>>>>

\documentclass[preview, border=1mm]{standalone}
\usepackage{tikz} %Format quantum circuits
\usetikzlibrary{quantikz2}%Format quantum circuits
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools,physics}

\begin{document}
	\begin{quantikz} 
	\lstick{$q_0$} & \gate{H} & \gate{R_{Z} (x_{0})} & \gate[2,disable auto height]{ZZ(x_{0},x_{1})} &   \gate[3,disable auto height]{ZZ(x_{0},x_{2})} & \gate[4,disable auto height]{ZZ(x_{0},x_{3})} &  \gate[5,disable auto height]{ZZ(x_{0},x_{4})}   & &  & & & & & \\ 
	\lstick{$q_1$}& \gate{H}  & \gate{R_{Z} (x_{1})} & & & & & \gate[2,disable auto height]{ZZ(x_{1},x_{2})} & \gate[3,disable auto height]{ZZ(x_{1},x_{3})} & \gate[4,disable auto height]{ZZ(x_{1},x_{4})} & & & &\\
	\lstick{$q_2$}& \gate{H}  & \gate{R_{Z} (x_{2})} & & & & & & & &  \gate[2,disable auto height]{ZZ(x_{2},x_{3})} &  \gate[3,disable auto height]{ZZ(x_{2},x_{4})} & & \\
	\lstick{$q_3$}& \gate{H}  & \gate{R_{Z} (x_{3})} & & & & & & & & & & \gate[2,disable auto height]{ZZ(x_{3},x_{4})} & \\
	\lstick{$q_4$}& \gate{H}  & \gate{R_{Z} (x_{4})} & & & & & & & & & & & \\
	\end{quantikz}
\end{document}
